### 2018-01-02 icde/revision/sec-app.tex

\section*{APPENDIX B: Detailed of Model}
\label{sec-exp-app}

\subsection{Ranking with Importance Assembling}
\label{subsec-ensemble}

%In our model, the importance of scholarly articles is defined as a combination of the prestige and popularity of its associated articles, venues and authors. Intuitively, prestige favors those with many citations soon after the publication of articles for citation component or associated articles for venue and author components, and popularity favors those with recent citations. Both prestige and popularity capture the temporal nature of entities in scholarly data.
In our model, the importance is defined as a combination of the prestige and popularity. Intuitively, prestige favors those with many citations soon after the publication of articles or associated articles of venues and authors, and popularity favors those with recent citations. Both prestige and popularity capture the temporal nature of entities. %in scholarly data.

@@

\begin{figure}[tb!]
\centering
%\includegraphics[scale=0.15]{fig/framework.eps}
\includegraphics[scale=0.35]{fig/example-graph.eps}
\vspace{-1ex}
\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
\vspace{-3ex}
\end{figure}

\begin{figure}[tb!]
\centering
%\includegraphics[scale=0.15]{fig/framework.eps}
\includegraphics[scale=0.35]{fig/example-ranking.eps}
\vspace{-1ex}
\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
\vspace{-3ex}
\end{figure}

@@

@@

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-pop}
Pop_c(v) = \sum_{{(u,v)\in E^c}} {e^{\sigma (T_0-T_u)}}.
\end{equation}
\end{small}
\noindent
Here $T_0$ is the current year, \ie the largest $T_u$ among all articles in $V^c$, $\sigma$ is the negative decaying factor used in Eq.~(\ref{eq-infl-weights}), and $e^{\sigma (T_0-T_u)}$ represents the freshness of citation $(u,v)$.

%Alternatively, one may want to define $Pop_c(v) = e^{\sigma \cdot (T_0-T_v)}$, \ie decaying with the publication year $T_v$ of article $v$ directly~\cite{sayyadi09,WalkerXKM07}. We propose to use the publication years $T_u$ of citations, instead of $T_v$, since $T_u$ reflects the ages of articles to some extent, \eg articles are probably cited in the next few years after publication(Fig.~\ref{fig-citation}).

Intuitively, the more recent citations an article has, the higher its popularity is, no matter how long it has been published.
Here popularity is introduced to capture the recent importance of articles, and articles with more recent citations have higher popularity scores. %, which is somehow biased to recent articles. Hence, we do not explicitly handle the bias for popularity computation.
%
%\marked{Different from $Peak_v$ in Eq.~(\ref{eq-infl-weights}), the bias of references has little impacts on the popularity. Moreover, the motivation of popularity is to assign higher ranks to articles of recent attention, which is somehow biased to recent articles. Hence, we do not explicitly handle the bias for popularity computation.}
%
Note that the popularity is also normalized such that the sum of  all articles is equal to $1$, similar to the prestige produced by TWPageRank.

@@

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-imp}
%Imp_c(v) = \sqrt{Prs_c(v) \cdot Pop_c(v)}.
Imp_c(v) = Prs_c(v)^\lambda Pop_c(v)^{1-\lambda},
\end{equation}
\end{small}
\noindent where $\lambda \in [0,1]$ is the importance weighting factor.
The rationales behind Eq.~(\ref{eq-imp}) are as follows. (a) Prestigious articles with many recent citations are ranked at the top, as researchers are very willing to find them; (b) Prestigious articles with rare current citations are ranked lower, as researchers may lose interests in these old articles; And (c) articles with many recent citations are ranked higher, as researchers have potential interests in those of recent attention.

%Here the prestige and popularity are equally weighted to produce the importance of an article, as we focus on query independent ranking. They may be properly weighted when the query information is available, which is beyond the scope of this work.

\begin{figure}[tb!]
\centering
%\includegraphics[scale=0.15]{fig/framework.eps}
\includegraphics[scale=0.15]{fig/framework-lite-2.eps}
\vspace{-1ex}
\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
\vspace{-3ex}
\end{figure}

@@

\vspace{-1ex}
\begin{small}
\begin{equation} \label{eq-infl-weights-v}
w_v(s,t)  = \sum_{u\in C(s), v\in C(t)} w(u,v).
\end{equation}
\end{small}
\noindent
Here, $C(s)$ and $C(t)$ are the sets of articles published in $s$ and $t$, respectively, and $w(u,v)$ is the impact weight of edge $(u, v)$ produced in the citation component.

@@

@@

%, which can be directly obtained from the citation component,
%to evaluate the authority of that author.

\eat{
\stitle{Affiliation ensemble}.
Recall that articles in our data are also associated with affiliation information. Following the way of the venue or author ensemble, we can derive another ensemble, \ie affiliation ensemble. However, we argue that the use of affiliation ensemble may have negative effects since the correlation between the importance of an article and the average authority of its affiliation(s) is not as strong as others such like authors and venues. As shown by the experimental study in Section~\ref{sec-exp},  the incorporation of the affiliation ensemble impairs the ranking accuracy. Hence, we choose not to use the affiliation ensemble in our model.
}

%\subsection{Ranking with Importance}
%{\label{subsec-eerank}}

@@

\vspace{-1ex}
\begin{small}
\begin{equation} \label{eq-ensemble}
R(v) =  \alpha R_c(v) + \beta R_v(v) + (1 - \alpha - \beta) R_a(v).
\end{equation}
\end{small}
\noindent Here aggregating parameters $\alpha$ and $\beta$ and value $(1 - \alpha - \beta)$ regularize the contributions of the citation, venue and author information,
which make our model be able to fit to the various ranking scenarios. As will be seen in the experiments, our model performs well in two reasonable ranking scenarios by using quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range.
Intuitively, these parameters indicate the intensity of the correlation between the importance of scholarly articles and the specific information.

>>>>

\section*{APPENDIX B: Ranking with Importance Assembling and Examples}
\label{sec-model-app}

In our model, the importance is defined as a combination of the prestige and popularity. Intuitively, prestige favors those with many citations soon after the publication of articles or associated articles of venues and authors, and popularity favors those with recent citations. Both prestige and popularity capture the temporal nature of entities. %in scholarly data.

@@

@@

%\markedb{We next illustrate how to generate the citation graph from the academic graph data with an example below.}

\begin{example} \label{eg-model-citation}
\markedb{Figure~\ref{fig-example-graph} shows a real-life example of the heterogeneous academic graph, which is drawn based on the following four articles as well as their citation relationships:}

\begin{small}
\bi
\item A: Ryan A. Rossi, and Nesreen K. Ahmed, ``Role Discovery in Networks," {\em TKDE}, 2015.
\item B: Charu C. Aggarwal, Yuchen Zhao, and Philip S. Yu, ``On the Use of Side Information for Mining Text Data," {\em TKDE}, 2014.
\item C: Charu C. Aggarwal, Yuchen Zhao, and Philip S. Yu, ``On Text Clustering with Side Information," In {\em ICDE}, 2012.
\item D: Shi Zhong, ``Efficient streaming text clustering," {\em Neural Networks}, 2005.
\ei
\end{small}

\markedb{The corresponding citation graph is also presented in Fig.~\ref{fig-example-graph} where the four nodes represent articles A, B, C and D, and edges represent the citations between them. Note that each node is also associated with time information (we omit the peak time on each node since it can only be computed when all the citations are given).}
\end{example}

\markedb{The importance of articles is then computed as follows.}

@@

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-pop-app}
Pop_c(v) = \sum_{{(u,v)\in E^c}} {e^{\sigma (T_0-T_u)}}.
\end{equation}
\end{small}
\noindent
Here $T_0$ is the current year, \ie the largest $T_u$ among all articles in $V^c$, $\sigma$ is the negative decaying factor used in Eq.~(\ref{eq-infl-weights}), and $e^{\sigma (T_0-T_u)}$ represents the freshness of citation $(u,v)$.

Intuitively, the more recent citations an article has, the higher its popularity is, no matter how long it has been published.
Here popularity is introduced to capture the recent importance of articles, and articles with more recent citations have higher popularity scores. 
%
Note that the popularity is also normalized such that the sum of  all articles is equal to $1$, similar to the prestige produced by TWPageRank.

@@

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-imp-app}
Imp_c(v) = Prs_c(v)^\lambda Pop_c(v)^{1-\lambda},
\end{equation}
\end{small}
\noindent where $\lambda \in [0,1]$ is the importance weighting factor.
The rationales behind Eq.~(\ref{eq-imp-app}) are as follows. (a) Prestigious articles with many recent citations are ranked at the top, as researchers are very willing to find them; (b) Prestigious articles with rare current citations are ranked lower, as researchers may lose interests in these old articles; And (c) articles with many recent citations are ranked higher, as researchers have potential interests in those of recent attention.

\begin{figure}[tb!]
\centering
\includegraphics[scale=0.34]{fig/example-graph.eps}
\vspace{-3.3ex}
\caption{\small An example of citation, venue and author citation graphs} \label{fig-example-graph}
\vspace{-3ex}
\end{figure}

@@

\vspace{-1ex}
\begin{small}
\begin{equation} \label{eq-infl-weights-v-app}
w_v(s,t)  = \sum_{u\in C(s), v\in C(t)} w(u,v).
\end{equation}
\end{small}
\noindent
Here, $C(s)$ and $C(t)$ are the sets of articles published in $s$ and $t$, respectively, and $w(u,v)$ is the impact weight of edge $(u, v)$ produced in the citation component.

\begin{example} \label{eg-model-venue}
\markedb{Recall the heterogeneous academic graph in Fig.~\ref{fig-example-graph}. Its corresponding venue graph is also presented. Note that two nodes in the venue graph are related to venue {\em TKDE} since each node denotes a venue in a specific year. There is an edge from nodes {\em TKDE-15} to {\em TKDE-14} since article A published in {\em TKDE-15} cites article B published in {\em TKDE-14}. And it is similar to derive other edges in the venue graph.}
\end{example}

@@

\begin{example} \label{eg-model-author}
\markedb{We also include the corresponding author citation graph in Fig.~\ref{fig-example-graph}. Observe that six links in the author citation graph are generated between authors \{{\em Ryan}, {\em Nesreen}\} to \{{\em Charu}, {\em Yuchen}, {\em Philip}\} given a single citation from articles A to B. And it is quite obvious that the number of edges in the author citation graph is much larger than the one in the citation graph, which verifies our claim above.}
\end{example}

@@

@@

\vspace{-1ex}
\begin{small}
\begin{equation} \label{eq-ensemble-app}
R(v) =  \alpha R_c(v) + \beta R_v(v) + (1 - \alpha - \beta) R_a(v).
\end{equation}
\end{small}
\noindent Here aggregating parameters $\alpha$ and $\beta$ and value $(1 - \alpha - \beta)$ regularize the contributions of the citation, venue and author information,
which make our model be able to fit to the various ranking scenarios. As will be seen in the experiments, our model performs well in two reasonable ranking scenarios by using quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range.
Intuitively, these parameters indicate the intensity of the correlation between the importance of scholarly articles and the specific information.

\begin{figure}[tb!]
\centering
\includegraphics[scale=0.37]{fig/example-ranking.eps}
\vspace{-2ex}
\caption{\small An example of importance assembling} \label{fig-example-ranking}
\vspace{-3ex}
\end{figure}

\begin{example} \label{eg-ranking}
\markedb{Figure~\ref{fig-example-ranking} illustrates an example of the importance assembling procedure. 
Consider an article $v$ published by authors $t$ and $u$ in venue $k$. 
(a) It first extracts the importance $c_v$ of article $v$ computed by the  citation component and properly scales $c_v$ to citation importance score $R_c(v)$.
Similarly, (b) it derives the venue importance score $R_v(v)$ based on the venue importance $v_k$ of venue $k$ computed  by the venue component.
(c) The author importance score $R_a(v)$ averages and scales the author importance $a_t$ and $a_u$ of authors $t$ and $u$ computed  by the author component.
Finally, (d) the three importance scores are aggregated to the final ranking score $R(v)$. }
\end{example}
